Panelökonometrie III: Lange Panels

### 2021-07-13 Drafts/Draft-Paneloekonometrie-1.Rmd
Commit panel drafts

>>>>

---
title: "Panelökonometrie I"
author: "Claudius"
date: "3/29/2021"
output: 
  bookdown::pdf_book:
    toc: true
    toc_depth: 4
    number_sections: true
    latex_engine: xelatex
    citation_package: natbib
    includes:
      in_header: "preamble_drafts.tex"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = "#>", message = FALSE, warning = FALSE)
knitr::opts_chunk$set(out.height = '75%', out.width = '75%', fig.align = 'center') 
```

### 2021-07-13 Drafts/Draft-Paneloekonometrie-3-LongPanels.Rmd
Commit panel drafts

>>>>

---
title: "Panelökonometrie III: Lange Panels"
author: "Claudius"
date: "3/29/2021"
output: 
  bookdown::pdf_book:
    toc: true
    toc_depth: 4
    number_sections: true
    latex_engine: xelatex
    citation_package: natbib
    includes:
      in_header: "preamble_drafts.tex"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = "#>", message = FALSE, warning = FALSE)
knitr::opts_chunk$set(out.height = '75%', out.width = '75%', fig.align = 'center') 
```
